Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeast Taiwan

### 2019-11-05 analysis/paper/paper.Rmd
updates about code

In archaeology, the landmarks are according to “type two” landmarks of Bookstein (1991), which define them as points located in the maximum of curvature or extreme points in morphology (Bookstein 1991; Zelditch et al. 2004).

were chosed  be applied to 3D objects not just limited to 2D that commonly applied to zooarchaeology and

the analysis of shape coordinates generated by the least-squares superimposition of configurations of landmarks

- related to the issue of specialization

- CV is hard to test, we apply some statistics testing for it

@@

```{r tidy-data}
# Once we have the jpgs, start from here
library(tidyverse)

@@

jpgs_imported_coo %>% 
  panel(., fac = phases_isect$phase)

pile(jpgs_imported_coo)
```

```{r EFA-analysis}
op <- efourier(jpgs_imported_coo, norm = FALSE)

@@

# Thin plate spline analysis (TPS)
# Thin plate splines (TPS) was used to compare average shapes and visualise the outline deformations required to pass from an extreme of the morphospace to the other.
# Deformation grids
png("Pottery_outlines/tps-pre-Euro-to-post-Euro.png", res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Post-European` , shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

png("Pottery_outlines/tps-pre-Euro-to-Chinese.png", res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Chinese Contact`, shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

@@

```{r get-data, eval = FALSE}
# Note the path that we need to use to access our data files when rendering this document
my_data <- read.csv(here::here('analysis/data/raw_data/my_csv_file.csv'))
```

```{r demo-plot, fig.cap="A plot of random numbers"}
plot(rnorm(10))
```

Figure \@ref(fig:demo-plot) shows how we can have a caption and cross-reference for a plot

```{r demo-inline-code}
x <- round(pi, 2)
```

Here is an example of inline code `r x` in the middle of a sentence.

>>>>

- related to the issue of specialization  
- CV is hard to test, we apply some statistics testing for it

@@

```{r tidy-data, eval=FALSE}
# Once we have the jpgs, start from here
library(tidyverse)

@@

saveRDS(jpgs_imported_coo,
        here::here("analysis/data/derived_data/jpgs_imported_coo.rds"))
```

```{r EFA-analysis}
jpgs_imported_coo <- read_rds(here::here("analysis/data/derived_data/jpgs_imported_coo.rds"))

op <- efourier(jpgs_imported_coo, norm = FALSE)

@@

# Thin plate spline analysis (TPS)
# Thin plate splines (TPS) was used to compare average shapes and visualise the outline deformations required to pass from an extreme of the morphospace to the other.
# Deformation grids
png(here::here("analysis/figures/tps-pre-Euro-to-post-Euro.png"), res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Post-European` , shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

png(here::here("analysis/figures/tps-pre-Euro-to-Chinese.png"), res = 300, w = 900, h = 900)
tps_grid(`Pre-European`, `Post-European`, shp.lwd = c(2, 2), shp.border = c("red", "blue"),
         amp = 1, grid.size = 18, legend = T)
dev.off()

@@
